Evidence of the necessity of isotopic precise calculation in fuel cycle calculation

### 2016-07-01 paper.tex
re-add caption on figure, add sep efficiency, stream composition, cyCLASS ref, facility labels, inventory explanation and value, clarify? the nn explanation

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Evidence of the necessity of isotopic precise calculation in fuel cycle
calculation}
\author{Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$, Meghan B. McGarry$^{*}$,
Arrielle C. Opotowsky$^{*}$ }

@@

%% PPHW: Need a reference to cyCLASS - perhaps tag a version and put a zip
%% file on figshare with a DOI.

\section{Study description}
This work compares the plutonium fraction required to build fresh MOX fuel
using three different stream mixing models in fuel fabrication: ``fixed mixing
ratio'', ``plutonium equivalent theory'', ``neural network'' \cite{CLASS_MLP}.
The first part of the study in focuses on the effect of decay on the isotopic
composition of the reprocessed plutonium and its impact on fuel fabrication
depending on the chosen stream mixing model.  The second part of the study,
compares the impact on fresh fuel compositions when used fuel is based on a
depletion calculation instead of a fixed recipe, using the neural network fuel
fabrication model, also including the impact of decay.

\subsection{Cycle}
This analysis is focused only on the second strata of EG29, represented by a single
PWR reactor using MOX fuel. After irradiation the uranium and the plutonium are
separated and reprocessed to fuel the next batch of MOX fuel for the PWR.
%% PPHW - must provide the separation parameters/efficiencies

@@

%% PPHW - must provide the composition of the ``good'' Pu
A stream of ``good'' quality plutonium coming from a hypothetical irradiated
SFR blanket is represented by a storage facility. 
%% PPHW - which facility?  which label - there are two.
The impact of the decay on this stored Pu
is limited, as the content in $^{241}$Pu is almost negligible.  In order to
build the first batch of fuel, an initial quantity of stored Pu has also been provided.
%% PPHW - how much?
In order to limit the effect of decay of this storage the initial inventory have been
tuned to be as small as possible, preventing any unnecessary accumulation of plutonium.
%% PPHW - is this about the initial inventory or the capacity of the storage facility
%%      - the latter seems to be about capacity

\subsection{Fabrication model}
Three different ways to model the fuel fabrication have been used: ``fix mixing
ratio'', ``Pu-equivalent'' and ``neural network''.
The fix mixing ratio is based on a user-defined ratio for the different stream mixing. The
``Pu-equivalent'' model finds the mixing ratio that results in an initial reactivity
that matches that of the requested MOX fuel recipe.  This ratio may change as the 
composition of the incoming streams changes.  As the requested fuel
composition corresponds to the fuel composition built with the ''fix mixing
ratio`` model, the results of those 2 models are expected to be similar.
The ``neural network'' model attempts to achieve a given reactivity at the end of a 
life for a given batch of fuel ($50~$GWd/t in this study). The
$<k_{infty}>$ used in this study is 1.034 \cite{???}. The neural network in this
model has been pre-trained on several different depletion calculations,
allowing it to predict the correct plutonium fraction required, depending
on the composition of that plutonium.

%% PPHW - is this end of cycle reactivity of the whole core for a multi-batch core?
%%      - or is it end of life reactivity for a given batch?
%%      - 1.034 and 50 GWd/t don't seem to go together

@@

The second part of the study compares the amount of plutonium require to build
the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
the recipe based output composition versus a compisition calculated by depletion.
To caluclate the depletion for each fuel batch loaded in the PWR reactor, another 
neural network is used to predict the macroscopic cross section of the
fuel \cite{NN_CLASS} (only fission, capture and n,2n reactions are considered). The
depletion calculation is done renormalizing the neutron flux to maintain a
constant power in the reactor.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{nodecay_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
  using the 3 predicted models, without considering decay.}
  \label{fig:nod}
\end{figure}

%% PPHW - need better figure legend text so that readers know what they are
%% looking at

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{decay_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
  using the 3 prediction models, with and without decay enable.}
  \label{fig:d}
\end{figure}

%% PPHW - need better color and symbol choices to facilitate comparison
%%      - different models use different colors and decay/no decay uses
%%      -  different symbols (for example)

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{irradiation_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
  using the ``neural network'' prediction models, with decay enable using recipe
based spent fuel composition and recalculated spent fuel composition.}
  \label{fig:depletion}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{MOX_pu_composition.png}
  \caption{Evolution of the composition of the plutonium in the fresh PWR-MOX fuel
  using the ``neural network'' prediction models, with decay enable using recipe
based spent fuel composition and recalculated spent fuel composition.}
  \label{fig:depletioncompo}
\end{figure}

>>>>

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Evidence of the necessity of isotopic precise calculation in fuel cycle
calculation}
\author{ Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$ }

@@

\section{Study description}

This work compares the plutonium fraction required to build fresh MOX fuel
using three different stream mixing models in fuel fabrication: ``fixed mixing
ratio'', ``plutonium equivalent theory'', ``neural network'' \cite{Leniau2015125}.
The first part of the study in focuses on the effect of decay on the isotopic
composition of the reprocessed plutonium and its impact on fuel fabrication
depending on the chosen stream mixing model.  The second part of the study,
compares the impact on fresh fuel compositions when used fuel is based on a
depletion calculation instead of a fixed recipe, using the neural network fuel
fabrication model, also including the impact of decay.

\subsection{Cycle}

This analysis is focused only on the second strata of EG29, represented by a
single PWR reactor using MOX fuel. After irradiation the uranium and the
plutonium are separated and reprocessed to fuel the next batch of MOX fuel for
the PWR. The separation efficiency is $0.988$. The separated U/Pu (``J1''
stream) is then separated into two sub-stream, one used for new PWR deployment
(``J1\_prime\_storage'' on Fig. \ref{fig:flow}) and the other one for the
production the new batch of MOX fuel (``J1\_second\_storage''). The respective
fraction of those sub-stream are $0.105$ and $0.895$.

@@

A stream (``E3'') of ``good'' quality plutonium coming from a hypothetical irradiated
SFR blanket is represented by a storage facility
(``E3\_second\_limited\_storage`` on Fig. \ref{fig:flow}).

\begin{table*}[htb]
  \centering
  \begin{tabular}{llllllllllll}\toprule
    Stream 
    & $^{234}$U   & $^{235}$U   & $^{236}$U   & $^{238}$U   
    & $^{238}$Pu  & $^{239}$Pu  & $^{240}$Pu  & $^{241}$Pu  & $^{242}$Pu 
    & $^{241}$Am  & F.P. \\ \midrule
    E3 [\%]
    & $0.002$   & $0.203$    & $0.083$   & $81.082$
    & $0.0087$  & $17.9764$  & $0.6166$  & $0.0216$  & $0.0007$
    & $0$         & $0$ \\
    J1 [\%]
    & $0$       & $0$        & $0$       & $93.632$
    & $0.1216$  & $2.7058$   & $1.8193$  & $0.7402$  & $0.6833$
    & $0.2978$  & $0$ \\
    \bottomrule
  \end{tabular}
  \caption{Streams compositions in percentage by mass.}
  \label{tab:strem_compo}
\end{table*}

The impact of the decay on this stored Pu is limited, as the content in
$^{241}$Pu is almost negligible (see Tab. \ref{tab:stream_compo}).

In order to build the first batches of fuel, an initial quantity of 225t has
also been provided in the ``J1\_second\_storage'', which corresponds to 3 times
the requirement on ``J1'' stream to build the PWR-MOX fuel for full PWR
core.

\subsection{Fabrication model}
Three different ways to model the fuel fabrication have been used: ``fix mixing
ratio'', ``Pu-equivalent'' and ``neural network''.
The fix mixing ratio is based on a user-defined ratio for the J1 and E3 stream
mixing. The respective mixing ratio used for J1 and E3 stream are 
$0.8357$ and $0.1643$.
The ``Pu-equivalent'' model finds the mixing ratio that results in an initial
reactivity that matches that of the requested MOX fuel recipe.  This ratio may
change as the composition of the incoming streams changes.  As the requested
fuel composition corresponds to the fuel composition built with the ''fix mixing
ratio`` model, the results of those 2 models are expected to be similar.  The
``neural network'' model attempts to achieve a given reactivity at the  end of
cycle reactivity of the whole core for a multi-batch core ($50~$GWd/t in this
study). The $k_{infty}$ used in this study is 1.034, assuming the reactivity of
the full core is the mean reactivity of the batches. The neural network in this
model has been pre-trained on several different depletion calculations, allowing
it to predict the correct plutonium fraction required, depending on the
composition of that plutonium.

Because the neural network model allows only to mix a plutonium stream into a
uranium stream, slight modification have been made on the cycle: in both ``J1''
and ``E3'' streams uranium and plutonium are separated, the uranium and
plutonium sub-streams are mix together to build one stream of pure uranium and
one stream of pure plutonium.

@@

The second part of the study compares the amount of plutonium require to build
the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
the recipe based output composition versus a composition calculated by depletion.
To calculate the depletion for each fuel batch loaded in the PWR reactor, another 
neural network is used to predict the macroscopic cross section of the
fuel \cite{Leniau2015125} (only fission, capture and n,2n reactions are considered). The
depletion calculation is done renormalizing the neutron flux to maintain a
constant power in the reactor.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{nodecay_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
  using the 3 predicted models: ``fix mixing ratio'' (``fix'', blue), ``Pu-equivalent''
  (``Pu-eq'', green) and ``Neural Network'' (``NN'', red), without considering decay.}
  \label{fig:nod}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{decay_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
    using the 3 prediction models: ``fix mixing ratio'' (``fix'', blue),
    ``Pu-equivalent'' (``Pu-eq'', green) and ``Neural Network'' (``NN'', red),
    with (plain line) and without (dash line) decay enable.} 
  \label{fig:d}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{irradiation_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
    using the ``Neural Network'' prediction models, using recipe based spent
    fuel composition (red) and recalculated spent fuel composition (orange),
    with (plain line) and without (dash line) decay enable.}
  \label{fig:depletion}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{MOX_pu_composition.png}
  \caption{Evolution of the composition of the plutonium in the fresh PWR-MOX fuel
  using the ``Neural Network'' prediction models, with decay enable using recipe
  based spent fuel composition (plain line) and recalculated spent fuel
  composition (dash line).}
  \label{fig:depletioncompo}
\end{figure}
